Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-05-23 supplement.tex

\appendix
{\centering \relsize{+4}\textbf{Supplementary Material}\\ Fixed-Parameter Tractable Sampling\\ for RNA Design with Multiple Target Structures\\%
%{\relsize{-1}\BackupTitle}\\
}
\relsize{+1}

>>>>

\appendix
{\centering \relsize{+4}\textbf{Supplementary Material}\\[1em] Fixed-Parameter Tractable Sampling\\ for RNA Design with Multiple Target Structures\\%
%{\relsize{-1}\BackupTitle}\\
}
\relsize{+1}
